SAT Solving for Vesicle Traffic Systems in Cells

### 2017-06-16 paper/experiments.tex
local changes

We have implemented the encoding of the constraints
in the python interface of $\zthree$.
%
Our implementation supports several versions of the
models of vesicle traffic systems.
\todo{describe the variations}
\begin{itemize}
\item 
\end{itemize}

We have applied the tool for the above variations
for searching the vesicle traffic systems that satisfies
their corresponding properties.
%
\input{tbl-qf-graph}
In table~\ref{tbl:qf-results}

\todo{Make table for all sizes and variants of the tool}

>>>>

We have implemented the encoding of the constraints
in the python interface of $\zthree$.
%
Our implementation supports several versions of the
models of vesicle traffic systems.
\todo{describe the variations}
\begin{itemize}
\item 
\end{itemize}
%
Our tool allows user to choose a model and the size of
the network.
%
It builds the needed constraints and applies $\zthree$
on the constraints.
%
Our tool also translates the model found by $\zthree$
into a vesicle traffic system and presents a visual
output to the user.

We have applied the tool for the above variations
for searching the vesicle traffic systems that satisfies
their corresponding properties.
%
\input{tbl-qf-graph}
In table~\ref{tab:qf-graph}, we present the running times
for the search of vesicle traffic systems of sizes 2 to 10
that satisfies the model variants.
%
The experiments were done on a machine with ... processor 
and ... RAM.
%

%
$\zthree$ was able to solve the constraints up to 10
nodes.
%
